Robinson et al. 2020 Supplemental Information: Comparing the Radiocarbon and Tree-ring Records for the Upland US Southwest

### 2020-02-05 README.Rmd
added Zenodo badge

# robinson2020
[![Travis build status](https://travis-ci.org/people3k/robinson2020.svg?branch=master)](https://travis-ci.org/people3k/robinson2020)
[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/people3k/robinson2020/master?urlpath=rstudio)

>>>>

# robinson2020
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.3647599.svg)](https://doi.org/10.5281/zenodo.3647599)
[![Travis build status](https://travis-ci.org/people3k/robinson2020.svg?branch=master)](https://travis-ci.org/people3k/robinson2020)
[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/people3k/robinson2020/master?urlpath=rstudio)
